Urban characteristics associated with diurnal and nocturnal land surface temperature

### 2019-04-16 report/article.tex
Updates from Overleaf

\section{Introduction}
In a warming world, understanding the drivers of LST and the UHI will aid in adapting cities to mitigate urban heat for the health and well being of communities.
The 1995 Chicago heat wave, which killed more than 700 people\footnote{The 2003 European heatwave killed 70,000 \cite{Robine 2008} and the 2015 European heat wave increased mortality up to 30\% \cite{Vicedo-Cabrera 2016 in Wicki} }, is expected to become an annual occurrence by 2080 under current climate projections \cite{klinenberg2015heat}. 
Heat waves are exacerbated by the urban heat island (UHI) \cite{Wicki2017-fv, Echevarria_Icaza2016-fr}.
The UHI results from heat captured during the day being released during the night increasing nocturnal temperatures \cite{Oke 1987, Landsberg1981, Rotach2005(bubble)}.
Among other negative effects on a city's environmental quality, the UHI reduces the ability of people to cool off during the night and causes increased mortality \cite{Stone2006}.
The UHI is studied in two ways.
The first considers the air temperature using atmospheric station data \cite{Scott2016-lc, etc} while the other examines the land surface temperature (LST) using remote sensing \cite{imhoff, Peng2012-iy, Peng2018-cp, Zhou2014-wc, etc.}. 
Here, we study the LST because the spatial coverage enables comparative studies \cite{Hung2006-qy}.

@@

- include scatter of night vs day LST at 100m - also change the symbols for colorblind - remove background
\begin{figure}[h]
\begin{center}
\includegraphics[width=\linewidth]{fig/report/lst_night-vs-day_500.pdf}
\caption{The land surface temperature in $^o$C of the cities studied at a 500m square resolution}
\label{fig:scatter_lst}
\end{center}
\end{figure}
\subsection{Independent variables}
- present correlation matrix of independent variables

>>>>

\section{Introduction}
In a warming world, understanding the drivers of LST and the UHI will aid in adapting cities to mitigate urban heat for the health and well being of communities.
The 1995 Chicago heat wave, which killed more than 700 people\footnote{The 2003 European heatwave killed 70,000 \cite{Robine 2008} and the 2015 European heat wave increased mortality up to 30\% \cite{Vicedo-Cabrera 2016 in Wicki} }, is expectAZed to become an annual occurrence by 2080 under current climate projections \cite{klinenberg2015heat}. 
Heat waves are exacerbated by the urban heat island (UHI) \cite{Wicki2017-fv, Echevarria_Icaza2016-fr}.
The UHI results from heat captured during the day being released during the night increasing nocturnal temperatures \cite{Oke 1987, Landsberg1981, Rotach2005(bubble)}.
Among other negative effects on a city's environmental quality, the UHI reduces the ability of people to cool off during the night and causes increased mortality \cite{Stone2006}.
The UHI is studied in two ways.
The first considers the air temperature using atmospheric station data \cite{Scott2016-lc, etc} while the other examines the land surface temperature (LST) using remote sensing \cite{imhoff, Peng2012-iy, Peng2018-cp, Zhou2014-wc, etc.}. 
Here, we study the LST because the spatial coverage enables comparative studies \cite{Hung2006-qy}.

@@

- include scatter of night vs day LST at 100m - also change the symbols for colorblind - remove background
\begin{figure}[h]
\begin{center}
\includegraphics[width=\linewidth]{fig/report/lst_night-vs-day_500.png}
\caption{The land surface temperature in $^o$C of the cities studied at a 500m square resolution}
\label{fig:scatter_lst}
\end{center}
\end{figure}
\subsection{Independent variables}
- present correlation matrix of independent variables
